babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-09 article.tex
No abbrev

Tracer displays multiple summary statistics for each
estimated variable: the mean and its standard error, standard deviation,
variance, median, mode, geometric mean, 95\% HPD interval, auto-correlation
time and effective sample size. To obtain all these summary statistics 
of the estimated birth rate in \verb;babette;:

>>>>

Tracer displays multiple summary statistics for each
estimated variable: the mean and its standard error, standard deviation,
variance, median, mode, geometric mean, 95\% highest posterior density interval, 
auto-correlation time and effective sample size. To obtain all these summary statistics 
of, for example, the estimated birth rate in \verb;babette;:
